Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-16 writeup/gz_hubble_data.tex
Fixes several points in #89

@@

\begin{table*}
\center
\caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lclcrr}
\hline\hline
Survey &  $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                                   & 2100$-$2300 & \Vband{} and \Iband{}            & 0.03 & 710   & 8157  \\
COSMOS                                  & 2028        & \Iband{}                         & 0.05 & 6480  & 88530 \\
GEMS                                    & 2160$-$2286 & \Vband{} and \zband{}            & 0.03 & 800   & 9143  \\
GOODS                                   & 1000$-$2100 & \Bband, \Vband, \iband, \zband{} & 0.03 & 320   &   \\
\hspace{10pt} \emph{GOODS-N~2~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{2551}  \\
\hspace{10pt} \emph{GOODS-S~2~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{3593}  \\
\hspace{10pt} \emph{GOODS-N~5~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{6015}  \\
\hspace{10pt} \emph{GOODS-S~5~epoch}    & $-$         & $-$                              & $-$  & $-$   & \emph{5142}  \\

\hline
total                                   & $-$         & $-$                              & $-$  & 8310  & 130467  \\
\hline\hline
\end{tabular}
\end{table*}

@@

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
priority is spectroscopic redshifts; these were taken from the ACS-GC
\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
high-quality spectroscopic redshift in the ACS-GC is the primary option; if
none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
than 98\% are consistent at $\Delta z<0.001$, and so the order of selection
made no practical difference. If no spectroscopic redshifts were available,
the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.

>>>>

The properties of the individual surveys are as follows:

@@

\begin{table*}
\center
\caption{Summary of GZH imaging \label{tbl:gzh_numbers}}
\begin{tabular}{lllcrr}
\hline\hline
Survey &  Total $t_{\rm exp}$ & Filters & Resolution & Area & $N_{\rm galaxies}$ \\
 & [sec] & & [\arcsec/pix] & [arcmin$^2$] & \\
\hline
AEGIS                                   & 2100$-$2300  & \Vband, \Iband{}                 & 0.03 & 710                & 8157    \\
COSMOS                                  & 2028         & \Iband{}                         & 0.05 & 6480               & 88530   \\
GEMS                                    & 2160$-$2286  & \Vband, \zband{}                 & 0.03 & 800                & 9143    \\
GOODS                                   & $-$          & $-$                              & $-$  & $-$                & $-$     \\
\hspace{10pt} \emph{GOODS-N~2~epoch}    & 2100$-$4200  & \Vband, \iband                   & 0.03 & 320                & 2551    \\
\hspace{10pt} \emph{GOODS-S~2~epoch}    & 2100$-$4200  & \Vband, \zband                   & 0.03 & 320                & 3593    \\
\hspace{10pt} \emph{GOODS-N~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 6015    \\
\hspace{10pt} \emph{GOODS-S~5~epoch}    & 5100$-$10500 & \Bband, \Vband, \iband, \zband{} & 0.03 & $^{\prime\prime}$  & 5142    \\
\hline
total                                   & $-$          & $-$                              & $-$  & 8630 & 123131  \\
\hline\hline
\end{tabular}
\end{table*}

@@

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
priority is spectroscopic redshifts; these were taken from the ACS-GC
\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
high-quality spectroscopic redshift in the ACS-GC is the primary option; if
none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
than 98\% are consistent at $\Delta z<0.001$, and so the order of selection
made no practical difference. Those which are inconsistent ($\Delta z>0.001$) between any of the three catalogs are marked with a Boolean flag in the column $\tt z\_spec\_conflict\_flag$ in Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were available,
the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.
